---
title: "Wrangle and summarize child observed affect during the Lab-TAB"
output: html_notebook
---

# Copy files on Oak to Desktop
```{r}
file_origin <- 
  dir(
    path = "/Volumes/group/active/MoD/Behavioral_Videos",
    pattern = "^\\d{5}_\\d{8}$",
    full.names = TRUE
  )

file_destination <- "~/Desktop/MoD/MoD_private/data/coding_files/"

files <-
  list.files(
    path = file_origin,
    pattern = "^\\d{5}_FilebyFrame_USE.csv$",
    recursive = TRUE,
    full.names = TRUE
  )

file.copy(files, file_destination)
```
# Environment set up
```{r}
#Libraries
library(tidyverse)
library(psych)
library(ggpubr)
library(corrr)
library(ggcorrplot)

source("~/Desktop/MOD/MoD/winsorize.R")

#Files
affect_files  <-
  tibble(
    path = 
      list.files(
        path = file_destination,
        pattern = "^\\d{5}_FilebyFrame_USE.csv$",
        full.names = TRUE
      )
  )

cbq_file <- paste0("~/Box/Mooddata_Coordinating/MOD/Data/REDCap/CBQ/cbq_cbqem_total_scores_20210322.csv")

cbbPalette <- c(
  "#000000", 
  "#E69F00", 
  "#56B4E9", 
  "#009E73", 
  "#F0E442", 
  "#0072B2", 
  "#D55E00", 
  "#CC79A7"
)
```

# Read in data
```{r, warning=FALSE}
affect_data <-
  affect_files %>% 
  mutate(
    data = map(path, ~read_csv(., col_types = cols(.default = "c")))
  ) %>% 
  unnest(data) %>% 
  mutate(
    ID = str_extract(path, "\\d{5}")
  )

```

```{r}
affect_data_cl <-
  affect_data %>% 
  mutate(
    # merge variables with same meaning but different names
    phase = case_when(
      !is.na(episode_section.code01) ~ episode_section.code01,
      !is.na(episode_segment.code01) ~ episode_segment.code01
    ),
    phase.onset = case_when(
      !is.na(episode_section.onset) ~ episode_section.onset,
      !is.na(episode_segment.onset) ~ episode_segment.onset
    ),
    phase.offset = case_when(
      !is.na(episode_section.offset) ~ episode_section.offset,
      !is.na(episode_segment.offset) ~ episode_segment.offset
    )
  ) %>% 
  select(
    id = ID,
    episode = episode.code01,
    episode.onset,
    episode.offset,
    phase,
    phase.onset,
    phase.offset,
    arousal.onset,
    arousal.offset,
    arousal = arousal_s.code01,
    valence.onset,
    valence.offset,
    valence = valence.code01,
    valence_r.onset,
    valence_r.offset,
    valence_r = valence_r.code01,
    -path
  ) %>% 
  mutate(
    # use regex to extract tidy info for phase variable
    phase = str_replace(phase, "^\\w+_", ""),
    phase = str_replace(phase, "^\\w+\\r_", ""),
    phase = str_replace(phase, "^\\w+\\r\\r_", ""),
    arousal = str_replace(arousal, "^\\w+_\\w+-", ""),
    # if missing arousal offset, use phase offset
    arousal.offset = if_else(
      is.na(arousal.offset) & !is.na(arousal), phase.offset, arousal.offset
    ),
    # fix errors in data entry
    arousal = case_when(
      phase == "Baseline- 0" ~ str_replace(phase, "^\\w+-", ""),
      phase == "Baseline- 0.5" ~ str_replace(phase, "^\\w+-", ""),
      phase == "Baseline- 1.5" ~ str_replace(phase, "^\\w+-", ""),
      phase == "Baseline- 2" ~ str_replace(phase, "^\\w+-", ""),
      phase == "Recovery- 0" ~ str_replace(phase, "^\\w+-", ""),
      phase == "Recovery- 1" ~ str_replace(phase, "^\\w+-", ""),
      phase == "	Stressor- 1" ~ str_replace(phase, "^\\w+-", ""),
      phase == "	Stressor- 0" ~ str_replace(phase, "^\\w+-", ""),
      phase == "	Stressor- 2" ~ str_replace(phase, "^\\w+-", ""),
      TRUE ~ arousal
    ),
    phase = case_when(
      phase == "Baseline- 0.5" ~ "Baseline",
      phase == "Baseline- 1.5" ~ "Baseline",
      phase == "Baseline- 0" ~ "Baseline",
      phase == "Baseline- 2" ~ "Baseline",
      phase == "Stresor" ~ "Stressor",
      phase == "PC\n_Recovery" ~ "Recovery",
      phase == "Stressor- 1" ~ "Stressor",
      phase == "Stressor- 0" ~ "Stressor",
      phase == "Stressor- 2" ~ "Stressor",
      phase == "Recovery- 0" ~ "Recovery",
      phase == "Recovery- 1" ~ "Recovery",
      phase == "SM\n_Baseline" ~ "Baseline",
      phase == "SM\n_Recovery" ~ "Recovery",
      phase == "SM\n_Stressor" ~ "Stressor",
      phase == "Basline" ~ "Baseline",
      phase == "B\n_Baseline" ~ "Baseline",
      TRUE ~ phase
    )
  ) %>%
  mutate_at(
    vars(id, ends_with("set"), ends_with("_r"), valence, arousal),
    as.double
  ) %>% 
  # remove data not nested within an episode or phase
  # remove ID 10046 due to improper camera angle
  filter(!is.na(episode), !is.na(phase), id != 10046)
```

# Number of individuals and observations
10046 missing because of improper camera angle.
10717 and 10718 missing SM b/c child too distressed prior to start. 

```{r}
affect_data_cl %>% 
  distinct(id)
```

```{r}
affect_data_cl %>% 
  distinct(id, episode) %>% 
  count(episode)
```


```{r}
affect_data_cl %>% 
  distinct(id, episode, phase) %>% 
  count(episode, phase)
```

# Score valence

## Steps below:
###1. Calculate duration (in seconds) of each phase.
###2. Calculate duration of the code (e.g., "neutral").
###3. Calculate the proportion of the phase in which the code was active (e.g., .50 of the phase was coded as neutral).

```{r}
valence_data <-
  affect_data_cl %>% 
  mutate(
    valence.onset = case_when(
      is.na(valence.onset) & !is.na(valence_r.onset) ~ valence_r.onset,
      !is.na(valence.onset) & is.na(valence_r.onset) ~ valence.onset,
      TRUE ~ valence.onset
    ),
    valence.offset = case_when(
      is.na(valence.offset) & !is.na(valence_r.offset) ~ valence_r.offset,
      !is.na(valence.offset) & is.na(valence_r.offset) ~ valence.offset,
      TRUE ~ valence.offset
    ),
    valence = case_when(
      is.na(valence) & !is.na(valence_r) ~ valence_r,
      !is.na(valence) & is.na(valence_r) ~ valence,
      TRUE ~ valence
    )
  ) %>% 
  select(
    id,
    episode,
    phase,
    phase.onset,
    phase.offset,
    valence.onset,
    valence.offset,
    valence
  ) %>% 
  group_by(id, episode, phase) %>% 
  mutate(
    phase_dur = (phase.offset - phase.onset) / 1000,
    valence_dur = (valence.offset - valence.onset) / 1000,
    valence_prop = valence_dur / phase_dur
  ) %>% 
  ungroup() %>% 
  distinct(id, episode, phase, valence_dur, valence, valence_prop) %>% 
  group_by(id, episode, phase, valence) %>% 
  summarise(
    prop = mean(valence_prop, na.rm = TRUE)
  ) %>% 
  ungroup()
```

### 4. Create a weighted sum by multiplying valence code by proportion
```{r}
valence_data <-
  valence_data %>% 
  filter(valence != 999) %>% 
  mutate(
    valence_product = prop * valence
  ) %>% 
  group_by(id, episode, phase) %>% 
  summarise(
    valence = sum(valence_product, na.rm = TRUE)
  ) %>% 
  ungroup() %>% 
  mutate(
    episode = fct_relevel(
      episode,
      "PC", "NSL", "B", "SM"
    ),
    phase = fct_relevel(
      phase,
      "Baseline", "Stressor", "Recovery"
    )
  )
```

# Score arousal
### Arousal is coded as single score for entire phase; simply tidy data
```{r}
arousal_data <- 
  affect_data_cl %>% 
  filter(!is.na(arousal)) %>% 
  select(
    id,
    episode,
    phase,
    phase.onset,
    phase.offset,
    arousal
  ) %>% 
  distinct(id, episode, phase, .keep_all = TRUE)
```

# Merge scored and tidied valence and arousal data
```{r}
ad <-
  valence_data %>% 
  left_join(arousal_data, by = c("id", "episode", "phase")) %>% 
  mutate(
    episode = factor(
      episode,
      levels = c("B", "PC", "NSL", "SM")
    ),
    phase = factor(
      phase,
      levels = c("Baseline", "Stressor", "Recovery")
    ),
    # standardize scores
    valence_z = scale(valence, scale = TRUE),
    arousal_z = scale(arousal, scale = TRUE),
    phase_duration = (phase.offset - phase.onset) / 1000
  )  %>% 
  group_by(id, episode) %>% 
  mutate(
    episode_duration = sum(phase_duration, na.rm = TRUE)
  ) %>% 
  ungroup() %>% 
  dplyr::select(-phase.onset, -phase.offset)
```

# Histograms

### Durations
Checked outlier for scary mask duration. Child explored mask in recovery phase for a long time.
```{r}
ad %>% 
  ggplot(aes(phase_duration, fill = phase)) +
  geom_histogram() +
  facet_wrap(.~episode, scales = "free")
```

### Valence
```{r}
ad %>% 
  ggplot(aes(valence_z, fill = phase)) +
  geom_histogram(binwidth = .25) +
  facet_wrap(.~episode, scales = "free")

ad %>% 
  ggplot(aes(valence_z, fill = phase)) +
  geom_density(alpha = 1/2) +
  facet_wrap(.~episode, scales = "free")
```
### Arousal
```{r}
ad %>% 
  ggplot(aes(arousal, fill = phase)) +
  geom_histogram(binwidth = .5) +
  facet_wrap(.~episode, scales = "free")

ad %>% 
  ggplot(aes(arousal, fill = phase)) +
  geom_density(alpha = 1/2) +
  facet_wrap(.~episode, scales = "free")
```
# Winsorize outliers
```{r}
ad <-
  ad %>% 
  mutate(
    valence = winsorize(valence, product = 3),
    valence_z = winsorize(valence_z, product = 3)
  )
```

# Create wide format version of data
```{r}
ad_wf_EP <-
  ad %>% 
  dplyr::select(
    id, 
    episode, 
    phase,
    phase_duration,
    episode_duration,
    valence_z, 
    arousal_z
  ) %>% 
  pivot_wider(
    names_from = c(episode, phase),
    values_from = c(phase_duration:arousal_z)
  )

ad_wf_E <- 
  ad %>% 
  group_by(id, episode) %>% 
  summarise_at(
    vars(valence:last_col()),
    funs(mean), na.rm = TRUE
  ) %>% 
  dplyr::select(
    id, 
    episode, 
    episode_duration,
    valence_z, 
    arousal
  ) %>% 
  pivot_wider(
    names_from = c(episode),
    values_from = c(episode_duration:arousal)
  ) %>% 
  ungroup()
```

# Correlations

## Everything
```{r}
ad_corrr <- 
  ad_wf_EP %>% 
  dplyr::select(valence_z_NSL_Baseline: last_col()) %>% 
  correlate() %>% 
  shave() %>% 
  fashion()

ad_corrr
```

```{r}
ad_wf_EP %>% 
  dplyr::select(valence_z_NSL_Baseline: last_col()) %>% 
  rename_at(
    vars(contains("_z_")),
    funs(str_replace(., "_z_", "_"))
  ) %>% 
  na.omit() %>% 
  cor() %>% 
  ggcorrplot(outline.color = "white", type = "lower")

ggsave(
  "~/Box/lucy_king_files/MoD/temperament/figures/labtab_all_corr.png",
  dpi = 500,
  height = 6,
  width = 8.5
)
```


## On average across episodes
```{r}
ad_wf_E %>% 
  dplyr::select(valence_z_B:last_col()) %>% 
  correlate() %>% 
  shave() %>% 
  fashion()
```

```{r}
ad_wf_E %>% 
  dplyr::select(valence_z_B: last_col()) %>% 
  rename_at(
    vars(contains("_z_")),
    funs(str_replace(., "_z_", "_"))
  ) %>% 
  na.omit() %>% 
  cor() %>% 
  ggcorrplot(outline.color = "white", type = "lower")

ggsave(
  "~/Box/lucy_king_files/MoD/temperament/figures/labtab_mean_episode_corr.png",
  dpi = 500,
  height = 6,
  width = 8.5
)
```
  
## At baseline
```{r}
ad_wf_EP %>% 
  dplyr::select(contains("Baseline")) %>% 
  dplyr::select(valence_z_Baseline_NSL: last_col()) %>% 
  correlate() %>% 
  shave() %>% 
  fashion()
```

```{r}
ad_wf_EP %>% 
  dplyr::select(contains("Baseline")) %>% 
  dplyr::select(valence_z_NSL_Baseline: last_col()) %>% 
  rename_at(
    vars(contains("_z_")),
    funs(str_replace(., "_z_", ""))
  ) %>% 
  na.omit() %>% 
  cor() %>% 
  ggcorrplot(outline.color = "white", type = "lower")

ggsave(
  "~/Box/lucy_king_files/MoD/temperament/figures/labtab_baseline_corr.png",
  dpi = 500,
  height = 6,
  width = 8.5
)
```


## At stressor
```{r}
ad_wf_EP %>% 
  dplyr::select(contains("Stressor")) %>% 
  dplyr::select(valence_z_Stressor_NSL: last_col()) %>% 
  correlate() %>% 
  shave() %>% 
  fashion() 
```
```{r}
ad_wf_EP %>% 
  dplyr::select(contains("Stressor")) %>% 
  dplyr::select(valence_z_NSL_Stressor: last_col()) %>% 
  rename_at(
    vars(contains("_z_")),
    funs(str_replace(., "_z_", ""))
  ) %>% 
  na.omit() %>% 
  cor() %>% 
  ggcorrplot(outline.color = "white", type = "lower")

ggsave(
  "~/Box/lucy_king_files/MoD/temperament/figures/labtab_stressor_corr.png",
  dpi = 500,
  height = 6,
  width = 8.5
)
```


## At recovery
```{r}
ad_wf_EP %>% 
  dplyr::select(contains("Recovery")) %>% 
  dplyr::select(valence_z_Recovery_NSL: last_col()) %>% 
  correlate() %>% 
  shave() %>% 
  fashion() 
```

```{r}
ad_wf_EP %>% 
  dplyr::select(contains("Recovery")) %>% 
  dplyr::select(valence_z_NSL_Recovery: last_col()) %>% 
  rename_at(
    vars(contains("_z_")),
    funs(str_replace(., "_z_", ""))
  ) %>% 
  na.omit() %>% 
  cor() %>% 
  ggcorrplot(outline.color = "white", type = "lower")


ggsave(
  "~/Box/lucy_king_files/MoD/temperament/figures/labtab_recovery_corr.png",
  dpi = 500,
  height = 6,
  width = 8.5
)
```
## With parent-reported tempermament (CBQ)

### all subscales
```{r}
ad_wf_EP %>% 
  left_join(read_csv(cbq_file), by = "id") %>% 
  dplyr::select(valence_z_NSL_Baseline: last_col()) %>% 
  correlate() %>% 
  shave() %>% 
  fashion()
```
```{r}
ad_wf_EP %>% 
  left_join(read_csv(cbq_file), by = "id") %>% 
  dplyr::select(valence_z_NSL_Baseline: last_col()) %>% 
  rename_at(
    vars(contains("_z_")),
    funs(str_replace(., "_z_", "_"))
  ) %>% 
  na.omit() %>% 
  cor() %>% 
  ggcorrplot(outline.color = "white", type = "lower")

ggsave(
  "~/Box/lucy_king_files/MoD/temperament/figures/labtab_cbq_all_corr.png",
  dpi = 500,
  height = 10,
  width = 12
)
```

### negative affectivity`
```{r}
ad_wf_EP %>% 
  left_join(read_csv(cbq_file), by = "id") %>% 
  dplyr::select(valence_z_NSL_Baseline: arousal_z_SM_Stressor, cbq_negativeaff) %>% 
  correlate() %>% 
  shave() %>% 
  fashion()
```

# Visualize 

### Summarize means, SEs
```{r}
labtab_summary_E <-
  ad %>% 
  group_by(episode) %>% 
  summarise(
    n = n(),
    Valence = mean(valence_z, na.rm = TRUE),
    valence_sd = sd(valence_z, na.rm = TRUE),
    valence_se = valence_sd / sqrt(n),
    Arousal = mean(arousal, na.rm = TRUE),
    arousal_sd = sd(arousal, na.rm = TRUE),
    arousal_se = arousal_sd / sqrt(n)
  )

labtab_summary_EP <-
  ad %>% 
  group_by(episode, phase) %>% 
  summarise(
    n = n(),
    Valence = mean(valence_z, na.rm = TRUE),
    valence_sd = sd(valence_z, na.rm = TRUE),
    valence_se = valence_sd / sqrt(n),
    Arousal = mean(arousal, na.rm = TRUE),
    arousal_sd = sd(arousal, na.rm = TRUE),
    arousal_se = arousal_sd / sqrt(n)
  )
```


### Valence x arousal
```{r}
ad %>% 
  ggplot(aes(valence, arousal, color = phase)) +
  geom_jitter() +
  geom_smooth(method = "lm") +
  facet_wrap(.~episode, scales = "free")
```

### Valence by phase and episode
```{r}
labtab_summary_EP %>% 
  filter(episode != "B") %>% 
  ggplot(aes(phase, Valence, color = episode, shape = episode)) +
  geom_pointrange(
    aes(ymin = Valence - valence_se, ymax = Valence + valence_se),
    size = 1.25
  ) +
  geom_line(aes(group = episode), size = 2, show.legend = FALSE) +
  scale_colour_manual(
    name = "Episode",
    values=cbbPalette
  ) +
  scale_shape_manual(
     name = "Episode",
     values = c(16, 17, 15)
  ) +
  scale_y_continuous(breaks = seq.int(-.4, .4, .1)) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "right"
  ) +
  labs(
    x = NULL,
    y = "Valence",
    color = NULL,
    shape = NULL
  )
```

### Valence by episode
```{r}
labtab_summary_E %>% 
  filter(episode != "B") %>% 
  ggplot(aes(episode, Valence)) +
  geom_pointrange(
    aes(ymin = Valence - valence_se, ymax = Valence + valence_se),
    size = 1.25
  ) +
  geom_line(aes(group = 1), size = 2, show.legend = FALSE) +
  scale_y_continuous(breaks = seq.int(-.2, .10, .03)) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "right"
  ) +
  labs(
    x = NULL,
    y = "Valence",
    color = NULL,
    shape = NULL
  )
```

### Arousal by phase and episode
```{r}
labtab_summary_EP %>% 
  filter(episode != "B") %>% 
  ggplot(aes(phase, Arousal, color = episode, shape = episode)) +
  geom_pointrange(
    aes(ymin = Arousal - arousal_se, ymax = Arousal + arousal_se),
    size = 1.25
  ) +
  geom_line(aes(group = episode), size = 2, show.legend = FALSE) +
  scale_colour_manual(
    name = "Episode",
    values=cbbPalette
  ) +
  scale_shape_manual(
     name = "Episode",
     values = c(16, 17, 15)
  ) +
  scale_y_continuous(breaks = seq.int(-1, 1, .1)) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "right"
  ) +
  labs(
    x = NULL,
    y = "Arousal",
    color = NULL,
    shape = NULL
  )

mean(affect_data_cl$valence, na.rm = TRUE)
```

### Arousal by episode
```{r}
labtab_summary_E %>% 
  filter(episode != "B") %>% 
  ggplot(aes(episode, Arousal)) +
  geom_pointrange(
    aes(ymin = Arousal - arousal_se, ymax = Arousal + arousal_se),
    size = 1.25
  ) +
  geom_line(aes(group = 1), size = 2, show.legend = FALSE) +
  scale_y_continuous(breaks = seq.int(.4, .8, .05)) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "right"
  ) +
  labs(
    x = NULL,
    y = "Arousal",
    color = NULL,
    shape = NULL
  )
```

## Arousal and valence by phase by episode

```{r}
labtab_summary_EP_lf <- 
  ad %>% 
  dplyr::select(
    episode,
    phase, 
    valence_z,
    arousal_z
  ) %>% 
  pivot_longer(
    cols = valence_z:arousal_z,
    names_to = "dimension"
  ) %>% 
  group_by(episode, phase, dimension) %>% 
  summarise(
    n = n(),
    mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),
    se = sd / sqrt(n),
  )
```
```{r}
labtab_summary_EP_lf %>% 
  filter(episode != "B") %>% 
  ggplot(aes(phase, mean, color = dimension, shape = dimension)) +
  geom_pointrange(
    aes(ymin = mean - se, ymax = mean + se),
    size = 1
  ) +
  geom_line(aes(group = dimension), size = 2, show.legend = FALSE) +
  scale_colour_manual(
    name = "Dimension",
    values=cbbPalette
  ) +
  scale_shape_manual(
     name = "Dimension",
     values = c(16, 17, 15)
  ) +
  scale_y_continuous(breaks = seq.int(-1, .5, .25)) +
  theme_pubr() +
  theme(
    strip.text = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_text(size = 20),
    axis.text.y = element_text(size = 16),
    axis.text.x = element_text(size = 16, angle = 320, hjust = .1),
    legend.title = element_text(size = 18),
    legend.text = element_text(size = 16),
    legend.position = "right"
  ) +
  labs(
    x = NULL,
    y = "Mean affect value\n(standardized)",
    color = NULL,
    shape = NULL
  ) +
  facet_grid(.~episode)

ggsave(
  "~/Box/lucy_king_files/MoD/temperament/figures/labtab_affect_grid.png",
  dpi = 500,
  height = 6,
  width = 10
)
```

# Reliability

## Score second coder valence
```{r}
valence_data_r <-
  affect_data_cl %>% 
  mutate(
    valence_r.onset = case_when(
      is.na(valence.onset) & !is.na(valence_r.onset) ~ NA_real_,
      !is.na(valence.onset) & is.na(valence_r.onset) ~ NA_real_,
      TRUE ~ valence_r.onset
    ),
    valence_r.offset = case_when(
      is.na(valence.offset) & !is.na(valence_r.offset) ~ NA_real_,
      !is.na(valence.offset) & is.na(valence_r.offset) ~ NA_real_,
      TRUE ~ valence_r.offset
    ),
    valence_r = case_when(
      is.na(valence) & !is.na(valence_r) ~ NA_real_,
      !is.na(valence) & is.na(valence_r) ~ NA_real_,
      TRUE ~ valence_r
    )
  ) %>% 
  select(
    id,
    episode,
    phase,
    phase.onset,
    phase.offset,
    valence_r.onset,
    valence_r.offset,
    valence_r
  ) %>% 
  group_by(id, episode, phase) %>% 
  mutate(
    phase_r_dur = (phase.offset - phase.onset) / 1000,
    valence_r_dur = (valence_r.offset - valence_r.onset) / 1000,
    valence_r_prop = valence_r_dur / phase_r_dur
  ) %>% 
  ungroup() %>% 
  distinct(id, episode, phase, valence_r_dur, valence_r, valence_r_prop) %>% 
  group_by(id, episode, phase, valence_r) %>% 
  summarise(
    prop_r = mean(valence_r_prop, na.rm = TRUE)
  ) %>% 
  ungroup()
```
  
```{r}
valence_data_r <-
  valence_data_r %>% 
  filter(valence_r != 999) %>% 
  mutate(
    valence_product_r = prop_r * valence_r
  ) %>% 
  group_by(id, episode, phase) %>% 
  summarise(
    valence_r = sum(valence_product_r, na.rm = TRUE)
  ) %>% 
  ungroup() %>% 
  mutate(
    episode = fct_relevel(
      episode,
      "PC", "NSL", "B", "SM"
    ),
    phase = fct_relevel(
      phase,
      "Baseline", "Stressor", "Recovery"
    )
  )
```  

## coder ICC for valence
```{r}
valence_data %>% 
  left_join(valence_data_r, by = c("id", "episode", "phase")) %>% 
  dplyr::select(
    valence,
    valence_r
  ) %>% 
  psych::ICC()
```

# Export data
```{r}
write_csv(ad_wf_EP, "~/Box/Mooddata_Coordinating/MOD/Data/Behavioral/labtab_cleaned_wf_20210712.csv")
write_csv(ad, "~/Box/Mooddata_Coordinating/MOD/Data/Behavioral/labtab_cleaned_lf_20210708.csv")
```

