---
title: "Score the Assessment of Parent and Child Adversity"
author: "Lucy King"
date: "6/23/2021"
output:
  pdf_document: default
  html_document: default
---

# Environment
```{r}
library(tidyverse)
library(purrr)
library(rlang)
library(reactable)
library(lubridate)

apca_raw_file <- "FILE PATH TO YOUR RAW APCA DATA IN CSV FORMAT"

options(
  reactable.theme = reactableTheme(
    style = list(
      fontFamily = "Arial")
  )
)
```

# Read in data
```{r}
a <-
  read_csv(apca_raw_file) %>% 
  mutate_at(
    vars(
      disaster:other1,
      other1_freq:other2,
      other2_freq:sexab_child_sev_dir
    ),
    as.numeric
  ) %>% 
  mutate_at(
    vars(contains("since_child")),
    as.numeric
  ) 

##replace decline to answer (88) and -888 (NA) values with NA
a[a == 88] <- NA
```

# Score APCA

## Total caregiver adversities
```{r}
# select the names of all variables measuring exposure to parent adversity
parent_types <-
  a %>% 
  dplyr::select(
    disas:death,
    bully:other1,
    other2,
    -ill_child_exp_dir
  ) %>% 
  names()
```

```{r}
# sum across these binary (1 = yes/0 = no) variables
a <- 
  a %>% 
  mutate(
    parent_num_types = 
      pmap_dbl(
      dplyr::select(., all_of(parent_types)),
      function(...) sum(c(...), na.rm = TRUE)
    )
  )
```

```{r}
# plot histogram of number of parent adversities
a %>% 
  ggplot(aes(parent_num_types)) +
  geom_histogram(binwidth = 2)
```

## Total subjective severity of caregiver adversities
```{r}
# select the names of all variables measuring parents' perceived severity of their adversities
parent_sev_ratings <- 
  a %>% 
  dplyr::select(contains("_sev")) %>% 
  dplyr::select(-contains("_sev_wit")) %>% 
  dplyr::select(-contains("_sev_dir")) %>% 
  dplyr::select(-ill_child_sev) %>% 
  names()
```

```{r}
# sum across perceived severity ratings for parental adversities
a <- 
  a %>% 
  mutate(
    parent_sum_sev = 
      pmap_dbl(
      dplyr::select(., all_of(parent_sev_ratings)),
      function(...) sum(c(...), na.rm = TRUE)
    )
  )
```

```{r}
# plot histogram of cumulative perceived severity of parental adversities 
a %>% 
  ggplot(aes(parent_sum_sev)) +
  geom_histogram(binwidth = 5)
```

## Total caregiver adversities since child's birth
```{r}
# select names of all variables measuring whether parental adversities occurred since birth of the focal child
since_child_types <-
  a %>% 
  dplyr::select(contains("since_child")) %>% 
  names()
```

```{r}
# sum across variables measuring parental adversities occured since child's birth (1=yes, 0-=no)
a <- 
  a %>% 
  mutate(
    since_child_num_types = 
      pmap_dbl(
      dplyr::select(., all_of(since_child_types)),
      function(...) sum(c(...), na.rm = TRUE)
    )
  )
```

```{r}
# plot histogram of number of parental adversities that occured since child's birth
a %>% 
  ggplot(aes(since_child_num_types)) +
  geom_histogram(binwidth = 5)
```

## Total subjective of severity caregiver adversities since child's birth

```{r}
# select names of parents' perceived severity ratings for only events that could have occurred since child's birth 
parent_sev_since_child <-
  a %>% 
  dplyr::select(contains("since_child")) %>% 
  rename_all(
    ~str_replace(., "_since_child", "_sev")
  ) %>% 
  dplyr::select(-since_child_num_types) %>% 
  names()
```

```{r}
# create a data frame of just the events and severity ratings that could have occurred since child's birth
a_sc <-
  a %>% 
  dplyr::select(id, all_of(since_child_types), all_of(parent_sev_since_child))

# select names of of events that could have occurred since child's birth
a_sc_names <- 
  a_sc %>% 
  dplyr::select(since_child_types) %>% 
  rename_all(
    ~str_replace(., "_since_child", "")
  ) %>% 
  names()

# use map to multiply event columns by severity columns that match the prefix value (i.e., the event type); if event did not happen since child's birth, product will be 0 
# then name these new product columns and add to the data frame 
a_sc <- 
  a_sc_names %>% 
  map(
    ~a_sc %>% 
      dplyr::select(matches(.x)) %>%
      reduce(`*`)) %>%
  set_names(
    paste0(a_sc_names, "since_child_sev")
  ) %>% 
  bind_cols(a_sc, .) 

```

```{r}
# merge "since_child" severity ratings with master data frame and compute summed score representing cumulative perceived severity of parental adversities occuring since child's birth
a <-
  a %>% 
  left_join(
    a_sc %>% 
      dplyr::select(id, ends_with("since_child_sev")), by = "id"
  ) 

since_child_sev_ratings <-
  a %>% 
  dplyr::select(contains("since_child_sev")) %>% 
  names()

a <-
  a %>% 
  mutate(
    parent_sum_sev_since_child = 
      pmap_dbl(
      dplyr::select(., all_of(since_child_sev_ratings)),
      function(...) sum(c(...), na.rm = TRUE)
    )
  )
```

```{r}
# plot historgram of cumulative perceived severity of parental adversities since the child's birth
a %>% 
  ggplot(aes(parent_sum_sev_since_child)) +
  geom_histogram(binwidth = 5)
```


## Total adversities during pregnancy and by trimester
```{r}
# select names of variables measuring parental exposure to adversity during all of pregnancy
preg_types <-
  a %>% 
  dplyr::select(ends_with("_preg")) %>% 
  names()

# select names of variables measuring parental exposure to adversity during the first trimester
trim1_types <-
  a %>% 
  dplyr::select(ends_with("_trim___1")) %>% 
  names()

# select names of variables measuring parental exposure to adversity during the second trimester
trim2_types <-
  a %>% 
  dplyr::select(ends_with("_trim___2")) %>% 
  names()

# select names of variables measuring parental exposure to adversity during the third trimester
trim3_types <-
  a %>% 
  dplyr::select(ends_with("_trim___3")) %>% 
  names()
```

```{r}
# sum across variables measuring parental exposure to adversity across pregnancy and during each trimester
a <-
  a %>% 
  mutate(
    preg_num_types = 
      pmap_dbl(
      dplyr::select(., all_of(preg_types)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    preg_trim1_num_types = 
      pmap_dbl(
      dplyr::select(., all_of(trim1_types)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    preg_trim2_num_types = 
      pmap_dbl(
      dplyr::select(., all_of(trim2_types)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    preg_trim3_num_types = 
      pmap_dbl(
      dplyr::select(., all_of(trim3_types)),
      function(...) sum(c(...), na.rm = TRUE)
    )
  )
```

```{r}
# plot histograms of parent exposure to adversity during pregnancy and in trimester
a %>% 
  dplyr::select(
    preg_num_types:preg_trim3_num_types
  ) %>% 
  pivot_longer(preg_num_types:preg_trim3_num_types) %>% 
  ggplot(aes(value)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(.~name, scales = "free")
```
 
## Total subjective severity of adversities during pregnancy and by trimester
```{r}
# select names of severity ratings for events that could have occurred during pregnancy 
sev_preg <-
  a %>% 
  dplyr::select(ends_with("_preg")) %>% 
  rename_all(
    ~str_replace(., "_preg", "_sev")
  ) %>% 
  names()
```

```{r}
# create a data frame of just the events and severity ratings that could have during pregnancy
a_p <-
  a %>% 
  dplyr::select(id, all_of(preg_types), all_of(sev_preg))

# select names of of events that could have occurred during pregnancy
a_p_names <- 
  a_p %>% 
  dplyr::select(preg_types) %>% 
  rename_all(
    ~str_replace(., "_preg", "")
  ) %>% 
  names()

# use map to multiply event columns by severity columns that match the prefix value (i.e., the event type); if event did not happen during pregnancy, product will be 0 
# then name these new product columns and add to the data frame 
a_p <- 
  a_p_names %>% 
  map(
    ~a_p %>% 
      dplyr::select(matches(.x)) %>%
      reduce(`*`)) %>%
  set_names(
    paste0(a_p_names, "_preg_sev")
  ) %>% 
  bind_cols(a_p, .) 
```

```{r}
# repeat for first trimester 
a_p1 <-
  a %>% 
  dplyr::select(id, all_of(trim1_types), all_of(sev_preg))

a_p1 <- 
  a_p_names %>% 
  map(
    ~a_p1 %>% 
      dplyr::select(matches(.x)) %>%
      reduce(`*`)) %>%
  set_names(
    paste0(a_p_names, "_trim1_sev")
  ) %>% 
  bind_cols(a_p1, .) 
```

```{r}
# repeat for second trimester 
a_p2 <-
  a %>% 
  dplyr::select(id, all_of(trim2_types), all_of(sev_preg))

a_p2 <- 
  a_p_names %>% 
  map(
    ~a_p2 %>% 
      dplyr::select(matches(.x)) %>%
      reduce(`*`)) %>%
  set_names(
    paste0(a_p_names, "_trim2_sev")
  ) %>% 
  bind_cols(a_p2, .) 
```

```{r}
# repeat for third trimester 
a_p3 <-
  a %>% 
  dplyr::select(id, all_of(trim3_types), all_of(sev_preg))

a_p3 <- 
  a_p_names %>% 
  map(
    ~a_p3 %>% 
      dplyr::select(matches(.x)) %>%
      reduce(`*`)) %>%
  set_names(
    paste0(a_p_names, "_trim3_sev")
  ) %>% 
  bind_cols(a_p3, .) 
```

```{r}
# merge pregnancy and trimester perceived parental severity ratings with master data frame 
a <-
  a %>% 
  left_join(
    a_p %>% 
      dplyr::select(id, ends_with("_preg_sev")), by = "id"
  ) %>% 
  left_join(
    a_p1 %>% 
      dplyr::select(id, ends_with("_trim1_sev")), by = "id"
  ) %>% 
  left_join(
    a_p2 %>% 
      dplyr::select(id, ends_with("_trim2_sev")), by = "id"
  ) %>% 
  left_join(
    a_p3 %>% 
      dplyr::select(id, ends_with("_trim3_sev")), by = "id"
  )
```

```{r}
# select names of variables measuring parental perceived severity of adversities during pregnancy and in each trimester
preg_sev_ratings <-
  a %>% 
  dplyr::select(ends_with("_preg_sev")) %>% 
  names()

trim1_sev_ratings <-
  a %>% 
  dplyr::select(ends_with("_trim1_sev")) %>% 
  names()

trim2_sev_ratings <-
  a %>% 
  dplyr::select(ends_with("_trim2_sev")) %>% 
  names()

trim3_sev_ratings <-
  a %>% 
  dplyr::select(ends_with("_trim3_sev")) %>% 
  names()
```

```{r}
# sum across variables meausuring parental perceived severity of adversity during prengnancy and in each trimester
a <-
  a %>% 
  mutate(
    sum_sev_preg = 
      pmap_dbl(
      dplyr::select(., all_of(preg_sev_ratings)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    sum_sev_trim1 = 
      pmap_dbl(
      dplyr::select(., all_of(trim1_sev_ratings)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    sum_sev_trim2 = 
      pmap_dbl(
      dplyr::select(., all_of(trim2_sev_ratings)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    sum_sev_trim3 = 
      pmap_dbl(
      dplyr::select(., all_of(trim3_sev_ratings)),
      function(...) sum(c(...), na.rm = TRUE)
    )
  )
```

```{r}
# plot histograms of cumulative  perceived severity of parental adversities during pregnancy and in each trimester
a %>% 
  dplyr::select(
    sum_sev_preg:sum_sev_trim3
  ) %>% 
  pivot_longer(sum_sev_preg:sum_sev_trim3) %>% 
  ggplot(aes(value)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(.~name, scales = "free")
```

## Adversities to which child was exposed (totat, direct, witnessed)

```{r}
# select names of variables measuring any type of child exposure to adversity, including direct adversity and witnessing of parental adversity
child_exp_types <-
  a %>% 
  dplyr::select(ends_with("child_exp_dir"), ends_with("child_exp_wit")) %>% 
  names()

# select names of variables measuring child witnessing of parental adversities
child_exp_wit_types <- 
  a %>% 
  dplyr::select(ends_with("child_exp_wit")) %>% 
  names()

#select names of variables measuring child direct exposure to adversity
child_exp_dir_types <- 
  a %>% 
  dplyr::select(ends_with("child_exp_dir")) %>% 
  names()
```

```{r}
# sum across variables measure total, witnessed, and direct child adversity
a <-
  a %>% 
  mutate(
    child_num_types = 
      pmap_dbl(
      dplyr::select(., all_of(child_exp_types)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    child_num_wit_types = 
      pmap_dbl(
      dplyr::select(., all_of(child_exp_wit_types)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    child_num_dir_types = 
      pmap_dbl(
      dplyr::select(., all_of(child_exp_dir_types)),
      function(...) sum(c(...), na.rm = TRUE)
    )
  )
```

```{r}
# plot histogram of child total, direct, and witnessed adversity
a %>% 
  ggplot(aes(child_num_types)) +
  geom_histogram(binwidth = 1)

a %>% 
  ggplot(aes(child_num_wit_types)) +
  geom_histogram(binwidth = 1)

a %>% 
  ggplot(aes(child_num_dir_types)) +
  geom_histogram(binwidth = 1)
```
## Total perceived severity of adversity to which child was exposed (direct or happened during child's lifetime)

```{r}
# select names of variables measuring parents' perceived severity for child of adversities, witnessed or direct
sev_child_ratings <-
  a %>% 
  dplyr::select(ends_with("_child_sev_dir"), ends_with("_child_sev_wit")) %>% 
  names()

# select names of variables parents' perceived severity for child of witnessed adversity 
sev_child_indir_ratings <- 
  a %>% 
  dplyr::select(ends_with("_child_sev_wit")) %>% 
  names()

# select names of variables parents' perceived severity for child of direct adversity
sev_child_dir_ratings <- 
  a %>% 
  dplyr::select(ends_with("_child_sev_dir")) %>% 
  names()
```

```{r}
# sum across variables measuring parents' perceived severity for child total, direct, and witnessed adversity
a <-
  a %>% 
  mutate(
    child_sum_sev = 
      pmap_dbl(
      dplyr::select(., all_of(sev_child_ratings)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    child_sum_sev_wit = pmap_dbl(
      dplyr::select(., all_of(sev_child_indir_ratings)),
      function(...) sum(c(...), na.rm = TRUE),
    child_sum_sev_dir =  pmap_dbl(
      dplyr::select(., all_of(sev_child_dir_ratings)),
      function(...) sum(c(...), na.rm = TRUE)
    )
    )
  )
```

```{r}
# plot histograms of parents' perceived severity for child of total, witnessed, and direct adversity
a %>% 
  ggplot(aes(child_sum_sev)) +
  geom_histogram(binwidth = 1)

a %>% 
  ggplot(aes(child_sum_sev_wit)) +
  geom_histogram(binwidth = 1)

a %>% 
  ggplot(aes(child_sum_sev_dir)) +
  geom_histogram(binwidth = 1)
```

## Wrangle parent ages of onset and offset of adversities

```{r}
# select names of parental age of onset variables
parent_age_onsets <- 
  a %>% 
  dplyr::select(contains("age_onset")) %>% 
  names()
```

```{r}
# reformat data for wrangling 
a_ages_lf <-
  a %>% 
  dplyr::select(
    id, 
    contains("age_onset"),
    contains("age_offset"),
    contains("ongoing"),
    preg_types,
    since_child_types,
    #these will be counted as child direct adversity
    -ill_child_age_onset, 
    -ill_child_age_offset, 
    -ill_child_ongoing,
    # rename for easier wrangling
    mentalill_age_onset = mental_ill_age_onset, # rename for easier wranglung
    mentalill_age_offset = mental_ill_age_offset,
    mentalill_preg = mental_ill_preg,
    mentalill_since = mental_ill_since_child,
    mentalill_ongoing = mental_ill_ongoing
  ) %>% 
  rename_with(
    .fn = ~str_replace(., "_since_child", "_since")
  ) %>% 
  rename_with(
    .fn = ~str_replace(., "_age_", "_")
  ) %>% 
  rename_with(
    .fn = ~str_replace(., "deathn", "death")
  ) %>% 
  pivot_longer(
    cols = other1_onset:last_col(),
    names_to = c("event_type",".value"),
    names_sep = "_"
  ) %>% 
  filter(!is.na(onset)) 
```

```{r}
# plot histogram of ages of onset for parental adversity
a_ages_lf %>% 
  ggplot(aes(onset)) +
  geom_histogram()
```

```{r}
# create variables indicating whether adversity occured during parent's child, adulthood, and prior to conception of the child
a_ages_lf <-
  a_ages_lf %>% 
  mutate(
    # any adversity that occurred prior to age 18 years
    parent_childhood = if_else(
      onset < 18, 1, 0
    ),
    # any adversity that occurred after age 18 years or is ongoing
    parent_adulthood = case_when(
      onset >= 18 ~ 1,
      offset >= 18 ~ 1,
      ongoing == 1 ~ 1,
      TRUE ~ 0
    ),
    # adversity that occurred after age 18 years, but did not occur since pregnant (i.e., did not occur in pregnancy or since the child's birth and is not ongoing)
    parent_precon = case_when(
      parent_adulthood == 1 & preg == 0 & ongoing == 0 & since == 0 ~ 1,
      parent_adulthood == 1 & is.na(preg) ~ 0,
      parent_adulthood == 1 & is.na(since) ~ 0,
      parent_adulthood == 1 & is.na(ongoing) ~ 0,
      TRUE ~ 0
    )
  )
```

```{r}
# return to wide format and join with master dataset 
a_ages_wf <-
  a_ages_lf %>% 
  dplyr::select(
    id, 
    event_type, 
    parent_childhood, 
    parent_adulthood,
    parent_precon
  ) %>% 
  pivot_wider(
    names_from = event_type,
    values_from = c(parent_childhood, parent_adulthood, parent_precon)
  )

a <-
  a %>% 
  left_join(a_ages_wf, by = "id")
```

## Total parent childhood, adulthood, and peconception adversity
```{r}
# select names of variables measuring parental exposure to adversity during childhood
parent_childhood_types <-
  a %>% 
  dplyr::select(contains("_childhood")) %>% 
  names()

# select names of variables measuring parental exposure to adversity during adulthood
parent_adulthood_types <-
  a %>% 
  dplyr::select(contains("_adulthood")) %>% 
  names()

# select names of variables measuring parental exposure to adversity prior to the conception of the focal child
parent_precon_types <-
  a %>% 
  dplyr::select(contains("_precon")) %>% 
  names()
```

```{r}
# sum across variables measuring parental exposure to adversity during childhood, adulthood, and prior to conception of the focal child
a <- 
  a %>% 
  mutate(
    parent_num_childhood = 
      pmap_dbl(
      dplyr::select(., all_of(parent_childhood_types)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    parent_num_adulthood = pmap_dbl(
      dplyr::select(., all_of(parent_adulthood_types)),
      function(...) sum(c(...), na.rm = TRUE)
    ),
    parent_num_precon= pmap_dbl(
      dplyr::select(., all_of(parent_precon_types)),
      function(...) sum(c(...), na.rm = TRUE)
    )
  )
```

```{r}
# plot histograms of parental total exposure to adversity in childhood, adulthood, and prior to conception 
a %>% 
  ggplot(aes(parent_num_childhood)) +
  geom_histogram(binwidth = 2)

a %>% 
  ggplot(aes(parent_num_adulthood)) +
  geom_histogram(binwidth = 2)

a %>% 
  ggplot(aes(parent_num_precon)) +
  geom_histogram(binwidth = 2)
```

## Wrangle child ages of indirect exposure
```{r}
# reformat data 
a_child_ages_lf <-
  a %>% 
  dplyr::select(id, contains("child_age_wit")) %>% 
  rename_with(
    ~str_replace(., "child_age_wit", "age"),
    ends_with("child_age_wit")
  ) %>% 
  rename_with(
    ~str_replace(., "child_age_wit_unit", "unit"),
    ends_with("child_age_wit_unit")
  ) %>% 
  rename(
    # for easier wrangling 
    mentalill_age = mental_ill_age,
    mentalill_unit = mental_ill_unit
  ) %>% 
  pivot_longer(
    cols = other1_age:last_col(),
    names_to = c("key", ".value"),
    names_sep = "_"
  ) %>% 
  mutate(
    # create single age in years variable
    age_years = case_when(
      unit == "1" ~ age / 12,
      unit == "2" ~ age,
      age == 0 ~ 0
    ),
    key = if_else(
      key == "mentalill", "mental_ill", key
    )
  ) %>% 
  filter(!is.na(age)) %>% 
  arrange(key) %>% 
  dplyr::select(
    id, 
    key,
    age_years
  )
```

```{r}
# plot histogram of child age of indirect exposure
a_child_ages_lf %>% 
  ggplot(aes(age_years)) +
  geom_histogram(binwidth = 2)

```

```{r}
# return to wide format
a_child_ages_wf <-
  a_child_ages_lf %>% 
  pivot_wider(
    names_from = key,
    values_from = age_years
  ) %>% 
  rename_at(
    vars(abort:last_col()),
    funs(paste0(., "_child_age"))
  )
```

## Wrangle child ages of direct exposure
```{r}
# reformat data
a_child_ages_dir_lf <-
  a %>% 
  dplyr::select(id, contains("child_age_dir")) %>% 
  rename_with(
    ~str_replace(., "child_age_dir", "age"),
    ends_with("child_age_dir")
  ) %>% 
  rename_with(
    ~str_replace(., "child_age_dir_unit", "unit"),
    ends_with("child_age_dir_unit")
  ) %>% 
  pivot_longer(
    cols = ill_age:last_col(),
    names_to = c("key", ".value"),
    names_sep = "_"
  ) %>% 
  mutate(
    # create single age in years variable
    age_years = case_when(
      unit == "1" ~ age / 12,
      unit == "2" ~ age,
      age == 0 ~ 0
    ),
  ) %>% 
  filter(!is.na(age)) %>% 
  arrange(key) %>% 
  dplyr::select(
    id, 
    key,
    age_years
  )

```

```{r}
# plot histogram of child age of direct exposure
a_child_ages_dir_lf %>% 
  ggplot(aes(age_years)) +
  geom_histogram(binwidth = 2)

```

```{r}
# return to wide format
a_child_ages_dir_wf <-
  a_child_ages_dir_lf %>% 
  pivot_wider(
    names_from = key,
    values_from = age_years
  ) %>% 
  rename_at(
    vars(acc:last_col()),
    funs(paste0(., "_child_age_dir"))
  )
```

# Export data
```{r}
write_csv(
  a, 
  "YOUR FILE PATH AND NAME FOR SCORED DATA"
)

```

