---
title: "Analyses for __Shared worlds and shared consequences: Initial validation of the Assessment of Parent and Child Adversity (APCA)__ (King et al., 2021)"
author: "Lucy King"
date: "5/14/2021"
output: html_document
---

# Environment
```{r}
library(tidyverse)
library(corrr)
library(performance)
library(parameters)
library(effectsize)
library(boot)
library(pscl)
library(ggpubr)
library(see)
library(msm)
library(facetscales)
library(DescTools)
library(gridExtra)
library(MASS)
library(BayesFactor)
library(bayestestR)

home <- "~/Box/Mooddata_Coordinating/MOD/Data/REDCap/"
demo_file <- paste0(home, "demographics/demo_cleaned_20210512.csv")
apca_file <- paste0(home, "APCA/apca_scored_20210514.csv")
cesd_file <- paste0(home, "CESD/cesd_scored_20210512.csv")
bai_file <- paste0(home, "BAI/bai_scored_20210512.csv")
cbcl_file <- paste0(home, "CBCL/preschool/cbcl_preschool_cleaned_20210423.csv")
ctq_file <- paste0(home, "CTQ/ctq_scored_20210512.csv")
bces_file <- paste0(home, "BCES/bces_scored_20210512.csv")
mod_bl_stress_file <- paste0(home, "MoD_Pregnancy_Project/baseline_stress_life_events.csv")
mod_perceived_stress_file <- paste0(home, "MoD_Pregnancy_Project/prenatal_stress_perceived.csv")
mod_perceived_stress_lf_file <- paste0(home, "MoD_Pregnancy_Project/prenatal_stress_perceived_lf.csv")

source("winsorize.r")

theme_mod <-
  theme_pubr() +
  theme(
    panel.grid = element_blank(),
    plot.title = element_text(size = 18, hjust = .5, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 18),
    legend.title = element_text(size = 20), 
    legend.text = element_text(size = 18),
    strip.text = element_text(size = 16, face = "bold"),
    strip.background = element_blank(),
    legend.position = "bottom"
  )

options(scipen = 999)
```

# Read in data
```{r}
d <-
  read_csv(demo_file) %>% 
  left_join(read_csv(apca_file), by = "id") %>% 
  left_join(read_csv(cesd_file), by = "id") %>% 
  left_join(read_csv(bai_file), by = "id") %>% 
  left_join(
    read_csv(cbcl_file) %>% 
      distinct(id, .keep_all = TRUE), 
    by = "id"
  ) %>% 
  left_join(read_csv(ctq_file), by = "id") %>% 
  left_join(read_csv(bces_file), by = "id") %>% 
  left_join(read_csv(mod_bl_stress_file), by = "id") %>% 
  left_join(read_csv(mod_perceived_stress_file), by = "id") 
```


```{r}
df <-
  d %>% 
  filter(!is.na(apca_timestamp)) %>% 
  mutate(
    primary_english = if_else(
      primarylang == "English", 1, 0
    )
  )

```

```{r}
df <-
  df %>% 
  group_by(id) %>% 
  # calculate total from life events checklist collected during pregnancy
  mutate(
    prenatal_life_events = sum(
      c(
        stress_death_lovd1,
        stress_accident,
        stress_bully,
        stress_divorce_parent,
        stress_divorce_self,
        stress_home_loss_parent,
        stress_home_loss_self,
        stress_job_loss_parent,
        stress_job_loss_self,
        stress_major_illness,
        stress_other_experience1,
        stress_other_experience2
      ),
      na.rm = TRUE
    ),
    prenatal_life_events = if_else(
      is.na(stress_death_lovd1), NA_real_, prenatal_life_events
    )
  ) %>% 
  ungroup()
```

# Sample descriptives

## Missing data
```{r}
df %>% 
  count(!is.na(ctq_total))

df %>% 
  count(!is.na(bces_total))

df %>% 
  count(!is.na(cesd_total))

df %>% 
  count(!is.na(bai_total))

df %>% 
  count(!is.na(total_problems_total))

df %>% 
  count(!is.na(prenatal_life_events))

df %>% 
  count(!is.na(prenatal_life_events))

```
## Internal consistency of measures
```{r}
# CTQ-SF
df %>% 
  dplyr::select(ctq_1:ctq_25) %>% 
  psych::alpha()
```
```{r}
# BCES
df %>% 
  dplyr::select(bce_1:bce_10) %>% 
  psych::alpha()
```

```{r}
# CESD
df %>% 
  dplyr::select(cesd_1:cesd_20) %>% 
  psych::alpha()

# % above clinical threshold
df %>% 
  count(cesd_total >= 16) %>% 
  mutate(per = n / sum(n))

```
```{r}
# BAI
df %>% 
  dplyr::select(bai_1:bai_21) %>% 
  psych::alpha()

# above clinical threshold
df  %>% 
  count(bai_total >= 16) %>%
  mutate(per = n / sum(n))
```

```{r}
# CBCL
df %>% 
  dplyr::select(c15_prob_1:c15_prob_99) %>% 
  psych::alpha()

df$c15_prob_1

# Above T-score (60) for borderline or clinical problems
df %>% 
  count(total_problems_tscore >= 60) %>% 
  mutate(per = n / sum(n))
```


## Continuous variables
```{r}
df %>% 
  summarise_at(
    vars(mom_age, child_age, inr_fpl),
    funs(mean, sd, min, max), na.rm = TRUE
  )
```

```{r}
df %>% 
  summarise_at(
    vars(
      parent_num_childhood,
      parent_num_precon,
      preg_num_types,
      since_child_num_types, 
      child_num_wit_types,
      child_num_dir_types
    ),
    funs(mean, sd, min, max), na.rm = TRUE
  )
```

```{r}
df %>% 
  summarise_at(
    vars(
      ctq_total, 
      bces_total,
      cesd_total, 
      bai_total,
      total_problems_total,
      parent_num_childhood,
      parent_num_precon,
      preg_num_types,
      since_child_num_types, 
      child_num_wit_types,
      child_num_dir_types
    ),
    funs(mean, sd, min, max), na.rm = TRUE
  )
```

### Identify outliers and winsorize 
```{r}
plot_histogram <- function(x) {
    x = sym(x)
  
    ggplot(df, aes(!!x)) +
    geom_histogram(binwidth = 1) +
    geom_vline(
      aes(
        xintercept = mean(
          !!x,
          na.rm = TRUE
        ) +
          (sd(
            !!x,
            na.rm = TRUE
          ) * 3)
      ),
      color = "red"
    ) +
    geom_vline(
      aes(
        xintercept = mean(
          !!x,
          na.rm = TRUE
        ) -
          (sd(
            !!x,
            na.rm = TRUE
          ) * 3)
      ),
      color = "red"
    )
}
```

```{r}
continuous_vars <- 
  df %>% 
  dplyr::select(
    parent_num_childhood,
    parent_num_precon,
    preg_num_types,
    since_child_num_types, 
    child_num_wit_types,
    child_num_dir_types,
    ctq_total, 
    bces_total,
    cesd_total, 
    bai_total,
    total_problems_total,
    prenatal_life_events
  ) %>% 
  names()

histograms_continuous <- map(continuous_vars, ~plot_histogram(.x))
histograms_continuous

```
```{r}
df <-
  df %>% 
  # winsorize to 3SD variables with outliers beyond that value
  mutate_at(
    vars(
      ctq_total,
      bai_total,
      bces_total,
      parent_num_childhood,
      preg_num_types,
      since_child_num_types,
      child_num_wit_types,
      child_num_dir_types,
      cesd_total,
      bai_total,
      total_problems_total,
      prenatal_life_events
    ),
    .funs = funs("W" = winsorize(., product = 3))
  ) %>% 
  # round winsorized count variables to nearest integer
  mutate_at(
    vars(
      parent_num_childhood_W,
      preg_num_types_W,
      since_child_num_types_W,
      child_num_wit_types_W,
      child_num_dir_types_W,
      prenatal_life_events_W
    ),
    .funs = funs(round(., digits = 0)) 
  )

```

## Categorical variables
```{r}
df %>% 
  count(mom_poc) %>% 
  mutate(per = n / sum(n))

df %>% 
  count(mom_white) %>% 
  mutate(per = n / sum(n))

df %>% 
  count(mom_black) %>% 
  mutate(per = n / sum(n))

df %>% 
  count(mom_asian) %>% 
  mutate(per = n / sum(n))

df %>% 
  count(mom_anative) %>% 
  mutate(per = n / sum(n))

df %>% 
  count(mom_pnative) %>% 
  mutate(per = n / sum(n))

df %>% 
  count(mom_other_race) %>% 
  mutate(per = n / sum(n))

df %>% 
  count(mom_decline_race) %>% 
  mutate(per = n / sum(n))
```

```{r}
df %>% 
  count(mom_latinx) %>% 
  mutate(per = n / sum(n))
```
```{r}
df %>% 
  count(primary_english) %>% 
  mutate(per = n / sum(n))
```


```{r}
df %>% 
  count(education) %>% 
  mutate(per = n / sum(n))

df %>% 
  mutate(
    education_re = case_when(
      education != "Bachelor's degree" & education != "Graduate degree" ~ "< 4yr college",
      education == "Bachelor's degree" ~ "Bachelor's degree",
      education == "Graduate degree" ~ "Graduate degree"
    )
  ) %>% 
  count(education_re) %>% 
  mutate(per = n / sum(n))
```
```{r}
df %>% 
  count(annual_income) %>% 
  mutate(per = n / sum(n)) %>% 
  arrange(per)
df %>% 
  count(inr_fpl <= 2) %>% 
  mutate(per = n / sum(n))
```
```{r}
df %>% 
  count(marital_status) %>% 
  mutate(per = n / sum(n))
```

```{r}
df %>% 
  count(child_male) %>% 
  mutate(per = n / sum(n))
```

## Correlations
```{r}
apca_corr <- 
  df %>% 
  dplyr::select(
    parent_num_childhood,
    parent_num_precon,
    preg_num_types,
    since_child_num_types,
    child_num_dir_types,
    child_num_wit_types,
    inr_fpl,
    mom_age,
    child_age
  ) %>% 
  correlate(method = "spearman", use = "pairwise.complete.obs") %>% 
  shave(upper = FALSE) %>% 
  fashion()

apca_corr

SpearmanRho(df$parent_num_childhood, df$child_num_dir_types, conf.level = .95)
SpearmanRho(df$parent_num_precon, df$child_num_dir_types, conf.level = .95)
SpearmanRho(df$preg_num_types, df$child_num_dir_types, conf.level = .95)
SpearmanRho(df$since_child_num_types, df$child_num_dir_types, conf.level = .95)

SpearmanRho(df$child_age, df$child_num_dir_types, conf.level = .95)
SpearmanRho(df$child_age, df$child_num_wit_types, conf.level = .95)

SpearmanRho(df$mom_age, df$parent_num_precon, conf.level = .95)

SpearmanRho(df$inr_fpl, df$parent_num_childhood, conf.level = .95, use = "complete.obs")
```


```{r}
apca_corr_plot <- 
  apca_corr %>% 
  gather(variable, value, -term) %>% 
  mutate(
    term = as.character(term),
    value_chr = as.character(value),
    value_chr = case_when(
      term == "child_num_wit_types" & variable == "child_num_dir_types" ~ ".38",
      variable == "child_num_wit_types" & term == "child_num_dir_types" ~ NA_character_,
      TRUE ~ value_chr
    ),
   value_num = as.numeric(value_chr)
  ) %>% 
  na.omit() %>% 
  mutate(
    term = factor(
      term,
      levels = c(
        "parent_num_childhood", 
        "parent_num_precon", 
        "preg_num_types", 
        "since_child_num_types",
        "child_num_wit_types",
        "child_num_dir_types",
        "inr_fpl",
        "mom_age",
        "child_age"
      ),
      labels = c(
        "Maternal childhood adversity",
        "Preconception adversity",
        "Prenatal adversity",
        "Maternal adversity since birth",
        "Child witnessed adversity",
        "Child direct adversity",
        "Income-to-FPL ratio",
        "Maternal age",
        "Child age"
      )
    ),
    variable = factor(
      variable,
      levels = c(
        "parent_num_childhood", 
        "parent_num_precon", 
        "preg_num_types", 
        "since_child_num_types",
        "child_num_wit_types",
        "child_num_dir_types",
        "inr_fpl",
        "mom_age",
        "child_age"
      ),
      labels = c(
        "Maternal childhood adversity",
        "Preconception adversity",
        "Prenatal adversity",
        "Maternal adversity since birth",
        "Child witnessed adversity",
        "Child direct adversity",
        "Income-to-FPL ratio",
        "Maternal age",
        "Child age"
      )
    )
  )
```

```{r}
apca_corr_plot %>% 
  ggplot(aes(x = fct_rev(variable), y = fct_rev(term))) +
  geom_tile(aes(fill = abs(value_num))) +
  geom_text(
    aes(label = value_chr), 
    size = 4
  ) +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    na.value = "white",
    midpoint = 0,
    limit = c(-1, 1),
    space = "Lab",
    name = "Spearman correlation\ncoefficient"
  ) +
  theme_void() +
  theme(
    axis.text.x = element_text(
      angle = 45,
      hjust = 1,
      vjust = 1,
      size = 12
    ),
    axis.text.y = element_text(
      size = 12,
      hjust = .9
    )
  ) 

ggsave(
  "~/Box/lucy_king_files/MoD/APCA/figures/correlations.png",
  dpi = 500,
  height = 5,
  width = 7.5
)
```

```{r}
df %>% 
  dplyr::select(
    cesd_total,
    bai_total_W,
    inr_fpl,
    mom_age,
    child_age
  ) %>% 
  correlate(method = "pearson", use = "complete.obs") %>% 
  shave(upper = FALSE) %>% 
  fashion()

cor.test(df$bai_total, df$cesd_total)
cor.test(df$mom_age, df$cesd_total)
cor.test(df$mom_age, df$bai_total)
```
```{r}
df %>% 
  dplyr::select(
    total_problems_total,
    bai_total_W,
    cesd_total,
    inr_fpl,
    mom_age,
    child_age
  ) %>% 
  correlate(method = "pearson", use = "complete.obs") %>% 
  shave(upper = FALSE) %>% 
  fashion()

cor.test(df$total_problems_total, df$cesd_total)
cor.test(df$total_problems_total, df$bai_total_W)
```

## t-tests
```{r}
t.test(df$parent_num_childhood ~ df$mom_poc)
t.test(df$parent_num_childhood ~ df$mom_latinx)

t.test(df$parent_num_precon ~ df$mom_poc)
t.test(df$parent_num_precon ~ df$mom_latinx)

t.test(df$preg_num_types ~ df$mom_poc)
t.test(df$preg_num_types ~ df$mom_latinx)
t.test(df$preg_num_types ~ df$child_male)

t.test(df$since_child_num_types ~ df$mom_poc)
t.test(df$since_child_num_types ~ df$mom_latinx)
t.test(df$since_child_num_types ~ df$child_male)

t.test(df$child_num_wit_types ~ df$mom_poc)
t.test(df$child_num_wit_types ~ df$mom_latinx)
t.test(df$child_num_wit_types ~ df$child_male)

t.test(df$child_num_dir_types ~ df$mom_poc)
t.test(df$child_num_dir_types ~ df$mom_latinx)
t.test(df$child_num_dir_types ~ df$child_male)
```

```{r}
t.test(df$cesd_total_W ~ df$mom_poc)
t.test(df$cesd_total_W ~ df$mom_latinx)
t.test(df$cesd_total_W ~ df$child_male)

t.test(df$bai_total_W ~ df$mom_poc)
t.test(df$bai_total_W ~ df$mom_latinx)
t.test(df$bai_total_W ~ df$child_male)

t.test(df$total_problems_total_W ~ df$mom_poc)
t.test(df$total_problems_total_W ~ df$mom_latinx)
t.test(df$total_problems_total_W ~ df$child_male)

```

## Additional APCA descriptives
```{r}
# proportion of maternal adversities since the child's birth that the child witnessed
df <-
  df %>% 
  mutate(
    apca_prop_child_wit = child_num_wit_types / since_child_num_types
  ) 

df %>% 
  summarise_at(
    vars(apca_prop_child_wit),
    funs(mean, median, sd, min, max), na.rm = TRUE
  )
```

# Primary statistical analyses

## Convergent validity

### CTQ 

#### Spearman's correlations
```{r}
SpearmanRho(df$parent_num_childhood_W, df$ctq_total_W, use = "complete.obs", conf.level = .95)
```

```{r}
SpearmanRho(df$parent_num_precon, df$ctq_total_W, use = "complete.obs", conf.level = .95)
SpearmanRho(df$preg_num_types_W, df$ctq_total_W, use = "complete.obs", conf.level = .95)
SpearmanRho(df$since_child_num_types_W, df$ctq_total_W, use = "complete.obs", conf.level = .95)
```

#### Bayes Factors
```{r}
childhood_ctq <- correlationBF(df$parent_num_childhood_W, df$ctq_total_W)
childhood_ctq <- describe_posterior(childhood_ctq, ci = 0.95)$BF

precon_ctq <- correlationBF(df$parent_num_precon, df$ctq_total_W)
precon_ctq <- describe_posterior(precon_ctq, ci = 0.95)$BF

preg_ctq <- correlationBF(df$preg_num_types_W, df$ctq_total_W)
preg_ctq <- describe_posterior(preg_ctq, ci = 0.95)$BF

since_ctq <- correlationBF(df$since_child_num_types_W, df$ctq_total_W)
since_ctq <-describe_posterior(since_ctq, ci = 0.95)$BF

con_BFs <-
  tibble(
    key = c(
      "parent_num_childhood",
      "parent_num_precon",
      "preg_num_types",
      "since_child_num_types"
    ),
    BF_ctq = c(
      childhood_ctq,
      precon_ctq,
      preg_ctq,
      since_ctq
    )
  )

con_BFs
```

Initially identified overdispersion using a poisson model. Used negative binomial regression to account for this. 

#### Negative binomial model

```{r}
glm.1 <- glm.nb(
  parent_num_childhood_W  ~ 
    scale(ctq_total_W, scale = FALSE),
  data = df
)
```

#### Diagnostics
```{r}
check_model(glm.1)
check_heteroscedasticity(glm.1)
```

#### Performance
```{r}
model_performance(glm.1)
```

#### Parameters
```{r}
model_parameters(
  glm.1,
  exponentiate = TRUE
) 
```

For each 1-unit increase in CTQ, the expected log count of APCA maternal cumulative adversity increases by .02. For each 1-unit increase in CTQ, the incidence rate for maternal cumulative adversity increased by 2%.

#### Plot expected counts
```{r}
# create new dataset with only CTQ
df_new <-
  df %>% 
  dplyr::select(
    ctq_total_W
  ) 

# generate predicted values
df_new$pred <-
  predict(
    glm.1,
    df_new,
    type = "response"
  )

# plot
ctq_plot <-
  df_new %>% 
  ggplot(aes(ctq_total_W, pred)) +
  geom_smooth(color = "black", size = 3) +
  geom_jitter2(
    data = df,
    aes(ctq_total_W, parent_num_childhood),
    size = 5, 
    alpha = 1/3,
    color = "black"
  ) +
  scale_y_continuous(breaks = seq.int(0, 25, 5)) +
  scale_x_continuous(breaks = seq.int(0, 50, 5)) +
  theme_mod +
  labs(
    title = "Convergent validity",
    x = "CTQ-SF\nMaternal childhood maltreatment",
    y = "APCA\nMaternal childhood adversity"
  )

ctq_plot

ggsave(
  "~/Box/lucy_king_files/MoD/APCA/figures/ctq_num_types.png",
  dpi = 500,
  height = 5,
  width = 6
)
```

### Life events measured in pregnancy

#### Spearman's correlations
```{r}
SpearmanRho(df$parent_num_childhood_W, df$prenatal_life_events_W, use = "complete.obs", conf.level = .95)
SpearmanRho(df$parent_num_precon, df$prenatal_life_events_W, use = "complete.obs", conf.level = .95)
```

#### Bayes Factors
```{r}
childhood_le <- correlationBF(df$parent_num_childhood_W, df$prenatal_life_events_W)
childhood_le  <- describe_posterior(childhood_le, ci = 0.95)$BF

precon_le  <- correlationBF(df$parent_num_precon, df$prenatal_life_events_W)
precon_le  <- describe_posterior(precon_le, ci = 0.95)$BF


con_BFs <-
  con_BFs %>% 
  cbind(
    BF_le = c(
      childhood_le,
      precon_le,
      NA_real_,
      NA_real_
    )
  )

con_BFs
```

#### Negative binomial model

```{r}
glm.2 <- glm.nb(
  parent_num_childhood_W  ~ 
    scale(prenatal_life_events_W, scale = FALSE),
  data = df
)

glm.3 <- glm.nb(
  parent_num_precon  ~ 
    scale(prenatal_life_events_W, scale = FALSE),
  data = df
)
```

#### Diagnostics
```{r}
check_model(glm.2)
check_heteroscedasticity(glm.2)

check_model(glm.3)
check_heteroscedasticity(glm.3)
```

#### Performance
```{r}
model_performance(glm.2)
model_performance(glm.3)
```

#### Parameters
```{r}
model_parameters(
  glm.2,
  exponentiate = TRUE
) 

model_parameters(
  glm.3,
  exponentiate = TRUE
) 
```

For each 1-unit increase in CTQ, the expected log count of APCA maternal cumulative adversity increases by .02. For each 1-unit increase in CTQ, the incidence rate for maternal cumulative adversity increased by 2%.

#### Plot expected counts
```{r}
# create new dataset with only CTQ
df_new <-
  df %>% 
  dplyr::select(
    ctq_total_W
  ) 

# generate predicted values
df_new$pred <-
  predict(
    glm.1,
    df_new,
    type = "response"
  )

# plot
ctq_plot <-
  df_new %>% 
  ggplot(aes(ctq_total_W, pred)) +
  geom_smooth(color = "black", size = 3) +
  geom_jitter2(
    data = df,
    aes(ctq_total_W, parent_num_childhood_W),
    size = 5, 
    alpha = 1/3,
    color = "black"
  ) +
  scale_y_continuous(breaks = seq.int(0, 14, 2)) +
  scale_x_continuous(breaks = seq.int(0, 50, 5)) +
  theme_mod +
  labs(
    title = "Convergent validity",
    x = "CTQ-SF\nMaternal childhood maltreatment",
    y = "APCA\nMaternal childhood adversity"
  )

ctq_plot

ggsave(
  "~/Box/lucy_king_files/MoD/APCA/figures/ctq_num_types.png",
  dpi = 500,
  height = 5,
  width = 6
)
```

## Discriminant validity

### BCES 

#### Spearman's correlations

```{r}
SpearmanRho(df$parent_num_childhood_W, df$bces_total_W, use = "complete.obs", conf.level = .95)

SpearmanRho(df$parent_num_precon, df$bces_total_W, use = "complete.obs", conf.level = .95)

SpearmanRho(df$preg_num_types_W, df$bces_total_W, use = "complete.obs", conf.level = .95)

SpearmanRho(df$since_child_num_types_W, df$bces_total_W, use = "complete.obs", conf.level = .95)
```

#### Bayes Factors
```{r}
childhood_bce <- correlationBF(df$parent_num_childhood_W, df$bces_total_W)
childhood_bce  <- describe_posterior(childhood_bce, ci = 0.95)$BF

precon_bce  <- correlationBF(df$parent_num_precon, df$bces_total_W)
precon_bce  <- describe_posterior(precon_bce, ci = 0.95)$BF

preg_bce <- correlationBF(df$preg_num_types_W, df$bces_total_W)
preg_bce <- describe_posterior(preg_bce, ci = 0.95)$BF

since_bce <- correlationBF(df$since_child_num_types_W, df$bces_total_W)
since_bce <-describe_posterior(since_bce, ci = 0.95)$BF

dis_BFs <-
  tibble(
    key = c(
      "parent_num_childhood",
      "parent_num_precon",
      "preg_num_types",
      "since_child_num_types"
    ),
    BF_bce = c(
      childhood_bce,
      precon_bce,
      preg_bce,
      since_bce
    )
  )

dis_BFs
```

#### Negative binomial model

```{r}
glm.4 <- glm.nb(
  parent_num_childhood  ~ 
    scale(bces_total_W, scale = FALSE),
  data = df
)
```

#### Diagnostics
```{r}
check_model(glm.4)
check_heteroscedasticity(glm.4)
```

#### Performance
```{r}
model_performance(glm.4)
```

#### Parameters
```{r}
model_parameters(
  glm.4,
  exponentiate = TRUE
) 
```
For each 1-unit increase in BCEs, the incidence rate for maternal cumulative adversity decreases by 22%.

#### Plot expected counts
```{r}
# create new dataset with BCEs only
df_new.1 <-
  df %>% 
  dplyr::select(
    bces_total_W
  )

# generate predicted values
df_new.1$pred <-
  predict(
    glm.2,
    df_new.1,
    type = "response"
  )

# plot
bces_plot <-
  df_new.1 %>% 
  ggplot(aes(bces_total_W, pred)) +
  geom_smooth(color = "black", size = 3, span = 1) +
  geom_jitter2(
    data = df,
    aes(bces_total_W, parent_num_childhood_W),
    size = 5, 
    alpha = 1/3,
    color = "black"
  ) +
  scale_y_continuous(breaks = seq.int(0, 15, 2)) +
  scale_x_continuous(breaks = seq.int(0, 10, 1)) +
  theme_mod +
  labs(
    title = "Discriminant validity",
    x = "BCEs\n Maternal positive childhood experiences",
    y = NULL
  )

bces_plot

ggsave(
  "~/Box/lucy_king_files/MoD/APCA/figures/bces_num_types.png",
  dpi = 500,
  height = 5,
  width = 4
)
```

### Arrange CTQ and BCEs plots
```{r}
ctq_bces_plots <- arrangeGrob(
  ctq_plot, 
  bces_plot, 
  nrow = 1
)

ggsave(
  "~/Box/lucy_king_files/MoD/APCA/figures/ctq_bces_apca_childhood.png",
  ctq_bces_plots,
  dpi = 1000,
  height = 5,
  width = 10
)
```

## Concurrent validity

### CESD 

#### Spearman's correlations
```{r}

SpearmanRho(df$parent_num_childhood_W, df$cesd_total_W, use = "complete.obs", conf.level = .95)

SpearmanRho(df$parent_num_precon, df$cesd_total_W, use = "complete.obs", conf.level = .95)

SpearmanRho(df$preg_num_types_W, df$cesd_total_W, use = "complete.obs", conf.level = .95)

SpearmanRho(df$since_child_num_types_W, df$cesd_total_W, use = "complete.obs", conf.level = .95)

```

#### Bayes Factors
```{r}
childhood_cesd <- correlationBF(df$parent_num_childhood_W, df$cesd_total_W)
childhood_cesd <- describe_posterior(childhood_cesd, ci = 0.95)$BF

precon_cesd <- correlationBF(df$parent_num_precon, df$cesd_total_W)
precon_cesd <- describe_posterior(precon_cesd, ci = 0.95)$BF

preg_cesd <- correlationBF(df$preg_num_types_W, df$cesd_total_W)
preg_cesd <- describe_posterior(preg_cesd, ci = 0.95)$BF

since_cesd <- correlationBF(df$since_child_num_types_W, df$cesd_total_W)
since_cesd <-describe_posterior(since_cesd, ci = 0.95)$BF

mp_BFs <-
  tibble(
    key = c(
      "parent_num_childhood",
      "parent_num_precon",
      "preg_num_types",
      "since_child_num_types"
    ),
    BF_cesd = c(
      childhood_cesd,
      precon_cesd,
      preg_cesd,
      since_cesd
    )
  )

mp_BFs
```

#### Multiple regression
```{r}
lm.1 <- lm(
  cesd_total_W ~
    parent_num_childhood_W +
    parent_num_precon +
    preg_num_types_W +
    since_child_num_types_W,
  data = df
)
```

```{r}
check_model(lm.1)
```

```{r}
model_performance(lm.1)
```

```{r}
model_parameters(lm.1)
model_parameters(lm.1, standardize = "refit")
```

### BAI

#### BAI Spearman's correlation

```{r}
SpearmanRho(df$parent_num_childhood_W, df$bai_total_W, use = "complete.obs", conf.level = .95)

SpearmanRho(df$parent_num_precon, df$bai_total_W, use = "complete.obs", conf.level = .95)

SpearmanRho(df$preg_num_types_W, df$bai_total_W, use = "complete.obs", conf.level = .95)

SpearmanRho(df$since_child_num_types_W, df$bai_total_W, use = "complete.obs", conf.level = .95)
```

#### Bayes Factors
```{r}
childhood_bai <- correlationBF(df$parent_num_childhood_W, df$bai_total_W)
childhood_bai<- describe_posterior(childhood_bai, ci = 0.95)$BF

precon_bai <- correlationBF(df$parent_num_precon, df$bai_total_W)
precon_bai <- describe_posterior(precon_bai, ci = 0.95)$BF

preg_bai <- correlationBF(df$preg_num_types_W, df$bai_total_W)
preg_bai <- describe_posterior(preg_bai, ci = 0.95)$BF

since_bai <- correlationBF(df$since_child_num_types_W, df$bai_total_W)
since_bai <-describe_posterior(since_bai, ci = 0.95)$BF

mp_BFs <-
  mp_BFs %>% 
  cbind(
    BF_bai = c(
      childhood_bai,
      precon_bai,
      preg_bai,
      since_bai
    )
  )

```
#### Multiple regression
```{r}
lm.2 <- lm(
 bai_total_W ~
    parent_num_childhood_W +
    parent_num_precon +
    preg_num_types_W +
    since_child_num_types_W,
  data = df
)
```

```{r}
check_model(lm.2)
```

```{r}
model_performance(lm.2)
```

```{r}
model_parameters(lm.2)
model_parameters(lm.2, standardize = "refit")
```


### BAI and CESD visualize associations

```{r}
scales_apca_cesd_bai_x <- list(
  "Childhood adversity" = scale_x_continuous(
    breaks = seq.int(0, 14, 2)
  ),
  "Preconception adversity" = scale_x_continuous(
    breaks = seq.int(0, 10, 2)
  ),
  "Prenatal adversity"= scale_x_continuous(
    breaks = seq.int(0, 8, 1)
  ),
  "Adversity since birth" = scale_x_continuous(
    breaks = seq.int(0, 12, 2)
  )
)

scales_apca_cesd_bai_y <- list(
  "Depression" = scale_y_continuous(
    breaks = seq.int(0, 30, 5)
  ),
  "Anxiety" = scale_y_continuous(
    breaks = seq.int(0, 25, 5)
  )
)


mp_BFs_lf <-
  mp_BFs %>% 
  rename(
    Depression = BF_cesd,
    Anxiety = BF_bai
  ) %>% 
  pivot_longer(
    cols = -key
  ) %>% 
  rename(
    adversity_type = key,
    symptoms_type = name,
    BF = value
  )
```

```{r}
df %>% 
  dplyr::select(
    Depression = cesd_total_W,
    Anxiety = bai_total_W,
    parent_num_childhood = parent_num_childhood_W,
    parent_num_precon,
    preg_num_types = preg_num_types_W,
    since_child_num_types = since_child_num_types_W
  ) %>% 
  pivot_longer(
    cols = parent_num_childhood:since_child_num_types,
    names_to = "adversity_type",
    values_to = "adversity_score"
  ) %>% 
  pivot_longer(
    cols = Depression:Anxiety,
    names_to = "symptoms_type",
    values_to = "symptoms_score"
  ) %>%
  left_join(mp_BFs_lf, by = c("adversity_type", "symptoms_type")) %>% 
  mutate(
    adversity_type = factor(
      adversity_type,
      levels = c(
        "parent_num_childhood",
        "parent_num_precon",
        "preg_num_types",
        "since_child_num_types"
      ),
      labels = c(
        "Childhood adversity",
        "Preconception adversity",
        "Prenatal adversity",
        "Adversity since birth"
      )
    ),
    BF_logic = case_when(
      BF > .33 & BF < 1 ~ "Anecdotal",
      BF >= 1 & BF < 3 ~ "Anecdotal",
      BF >= 3 & BF < 10 ~ "Moderate",
      BF >= 10 & BF < 30 ~ "Strong",
      BF >= 30 & BF < 100 ~ "Very strong",
      BF >= 100 ~ "Extreme"
    ),
    BF_logic = factor(
      BF_logic,
      levels = c("Anecdotal", "Moderate", "Strong", "Very strong", "Extreme")
    )
  ) %>% 
  ggplot(aes(adversity_score, symptoms_score)) +
  geom_jitter2(size = 4, alpha = 1/2, color = "black") +
  geom_smooth(
    method = "lm", 
    size = 4, 
    se = FALSE,
    aes(color = BF_logic)
  ) +
  scale_y_continuous(breaks = seq.int(0, 40, 5)) +
  scale_x_continuous(breaks = seq.int(0, 15, 1)) +
  scale_color_brewer(
    palette = "Oranges"
  ) +
  theme_grey() +
  theme(
    panel.grid = element_blank(),
    plot.title = element_text(size = 18, hjust = .5, face = "bold"),
    axis.title = element_text(size = 20),
    axis.text = element_text(size = 18),
    legend.title = element_text(size = 20), 
    legend.text = element_text(size = 18),
    strip.text.x = element_text(size = 16, face = "bold", color = "black"),
    strip.text.y = element_text(size = 20, face = "bold", color = "black"),
    strip.background = element_blank(),
    legend.position = "right"
  ) +
  labs(
    color = "Bayes Factor\n(Strength of evidence)",
    x = NULL,
    y = "Maternal symptoms"
  ) +
  facet_grid_sc(
    symptoms_type ~ adversity_type,
    scales = list(x = scales_apca_cesd_bai_x)
  )

ggsave(
  "~/Box/lucy_king_files/MoD/APCA/figures/cesd_bai_adversity.png",
  dpi = 1000,
  height = 6,
  width = 14.75
)

```

## Comparative convergent validity

### CTQ ~ CESD

```{r}
cor.test(df$ctq_total_W, df$cesd_total_W)

ctq_cesd<- correlationBF(df$ctq_total_W, df$cesd_total_W)
describe_posterior(ctq_cesd, ci = 0.95)$BF
```

### Life events measured in pregnancy ~ CESD

```{r}
SpearmanRho(df$prenatal_life_events_W, df$cesd_total_W, use = "complete.obs", conf.level = .95)

ple_cesd<- correlationBF(df$prenatal_life_events_W, df$cesd_total_W)
describe_posterior(ple_cesd, ci = 0.95)$BF
```

### CTQ ~ BAI
```{r}
cor.test(df$ctq_total_W, df$bai_total_W)

ctq_bai<- correlationBF(df$ctq_total_W, df$bai_total_W)
describe_posterior(ctq_bai, ci = 0.95)$BF
```

### Life events measured in pregnancy ~ BAI

```{r}
SpearmanRho(df$prenatal_life_events_W, df$bai_total_W, use = "complete.obs", conf.level = .95)

ple_bai <- correlationBF(df$prenatal_life_events_W, df$bai_total_W)
describe_posterior(ple_bai, ci = 0.95)$BF
```

### CBCL 


#### Spearman's correlations
```{r}
# maternal exposure
SpearmanRho(df$parent_num_types, df$total_problems_total, use = "complete.obs", conf.level = .95)

SpearmanRho(df$parent_num_childhood_W, df$total_problems_total, use = "complete.obs", conf.level = .95)

SpearmanRho(df$parent_num_precon, df$total_problems_total, use = "complete.obs", conf.level = .95)

SpearmanRho(df$preg_num_types_W, df$total_problems_total, use = "complete.obs", conf.level = .95)

SpearmanRho(df$since_child_num_types_W, df$total_problems_total, use = "complete.obs", conf.level = .95)


# child witnessing and exposure
SpearmanRho(df$child_num_wit_types_W, df$total_problems_total, use = "complete.obs", conf.level = .95)

SpearmanRho(df$child_num_dir_types_W, df$total_problems_total, use = "complete.obs", conf.level = .95)
```

#### Bayes Factors
```{r}
childhood_cbcl <- correlationBF(df$parent_num_childhood_W, df$total_problems_total)
childhood_cbcl <- describe_posterior(childhood_cbcl, ci = 0.95)$BF

precon_cbcl  <- correlationBF(df$parent_num_precon, df$total_problems_total)
precon_cbcl  <- describe_posterior(precon_cbcl, ci = 0.95)$BF

preg_cbcl  <- correlationBF(df$preg_num_types_W, df$total_problems_total)
preg_cbcl <- describe_posterior(preg_cbcl, ci = 0.95)$BF

since_cbcl  <- correlationBF(df$since_child_num_types_W, df$total_problems_total)
since_cbcl  <-describe_posterior(since_cbcl, ci = 0.95)$BF

wit_cbcl  <- correlationBF(df$child_num_wit_types_W, df$total_problems_total)
wit_cbcl  <-describe_posterior(wit_cbcl, ci = 0.95)$BF

dir_cbcl  <- correlationBF(df$child_num_dir_types_W, df$total_problems_total)
dir_cbcl  <-describe_posterior(dir_cbcl, ci = 0.95)$BF

cp_BFs <-
  tibble(
    key = c(
      "parent_num_childhood",
      "parent_num_precon",
      "preg_num_types",
      "since_child_num_types",
      "child_num_wit_types",
      "child_num_dir_types"
    ),
    BF_cbcl= c(
      childhood_cbcl,
      precon_cbcl,
      preg_cbcl,
      since_cbcl,
      wit_cbcl,
      dir_cbcl
    )
  )

cp_BFs

```

### CBCL visualize

```{r}
scales_apca_child_probs <- list(
  `Maternal cumulative adversity` = scale_x_continuous(
    breaks = seq.int(0, 25, 5)
  ),
  `Child direct adversity` = scale_x_continuous(
    breaks = seq.int(0, 4, 1)
  )
)

df %>% 
  dplyr::select(
    total_problems_total,
    `Maternal cumulative adversity` = parent_num_types,
    `Child direct adversity` = child_num_dir_types
  ) %>% 
  pivot_longer(
    cols = `Maternal cumulative adversity`:`Child direct adversity`
  ) %>% 
  mutate(
    name = factor(
      name,
      levels = c(
        "Maternal cumulative adversity",
        "Child direct adversity"
      )
    )
  ) %>% 
  ggplot(aes(value, total_problems_total)) +
  geom_jitter2(size = 5, alpha = 1/3) +
  geom_smooth(method = "glm", size = 3, color = "black", se = FALSE) +
  scale_y_continuous(breaks = seq.int(0, 70, 10)) +
  scale_x_continuous(breaks = seq.int(0, 25, 1)) +
  theme_mod +
  labs(
    x = "APCA score",
    y = "Child total behavioral\nand emotional problems"
  ) +
  facet_grid_sc(.~name, scales = list(x = scales_apca_child_probs))

ggsave(
  "~/Box/lucy_king_files/MoD/APCA/figures/cbcl_apca_scores.png",
  dpi = 500,
  height = 5,
  width = 11
)
```

### CBCL total problems regressions

### Fit model
```{r}
lm.4 <- lm(
  total_problems_total ~ 
    scale(cesd_total, scale = FALSE) +
    scale(bai_total, scale = FALSE),
  data = df
)

lm.5 <- lm(
  total_problems_total ~ 
    scale(cesd_total, scale = FALSE) +
    scale(bai_total, scale = FALSE) +
    scale(parent_num_childhood_W, scale = FALSE) +
    scale(parent_num_precon, scale = FALSE) +
    scale(preg_num_types_W) +
    scale(since_child_num_types_W),
  data = df
)


lm.6 <- lm(
  total_problems_total ~ 
    scale(cesd_total, scale = FALSE) +
    scale(bai_total, scale = FALSE) +
    scale(child_num_dir_types_W) +
    scale(child_num_wit_types_W),
  data = df
)

```

### Diagnostics
```{r}
check_model(lm.5)
check_model(lm.6)
```

### Performance
```{r}
lm.4_performance <- model_performance(lm.4)
lm.5_performance <- model_performance(lm.5)
lm.6_performance <- model_performance(lm.6)

# R-squared change for maternal adversity variables
lm.5_performance$R2_adjusted - lm.4_performance$R2

# R-squared change for child adversity variables
lm.6_performance$R2_adjusted - lm.4_performance$R2
```

### Parameters
```{r}
model_parameters(lm.5) 
model_parameters(lm.5, standardize = "refit")

model_parameters(lm.6) 
model_parameters(lm.6, standardize = "refit")
```
